The yaq Project: a Protocol for Scientific Instrumentation

### 2022-04-29 paper.tex

TCP

\subsection{TCP}

\subsection{Avro RPC}

AVRO-RPC

@@

configuration

>>>>

yaq is built on top of Apache Avro RPC \cite{AvroSpecification}.
Avro RPC is a Remote Procedure Call framework which allows interprocess communication between a client application and a daemon \(the server\) which has direct hardware access.
Avro provides an agreed upon standard for serialization of data and method calls from a remote \(client\) process.
The protocols defined by Avro are extensible, allowing daemons to define their own data types and declare additional messages that can be processed by the daemon.
Each daemon provides an Avro Protocol file \(avpr\) which provides a complete list of the types and allowed messages.

While Avro RPC itself is agnostic to transport layer, yaq specifies TCP sockets as the transport layer.
TCP socket libraries are ubiquitous, allowing for clients (or daemons) to be implemented in a variety of languages if required.
The use of TCP also works across standard networks, allowing for simple multi-machine instruments.
yaq uses ``stateful'' Avro RPC to allow multiple requests without requiring additional handshaking.

@@

In addition to the standard, yaq specifices schema for configuration options and for state that is persistent across restarts of a daemon.

\subsection{Properties and Traits}
